Reproducibility of published meta-analyses on clinical psychological interventions

### 2023-04-24 response_letter.Rmd

Interesting point that we missed checking. It seems that the OSF repository was created just before the paper was accepted (02/06/2019 created, 13/06/2019 accepted). It seems that the OSF repo was created upon request of the journal. We think that this deserves to be mentioned in the manuscript, so we have added the following text (see p.21, footnote 7):

>\textcolor{blue}{According to the repository timeline the project was created on 02/06/2019 and according to the journal’s article history the paper was published on 13/06/2019. It seems that the repository was created as a journal requirement.}

\RC{- The authors responded "No" and "Not Applicable" to these prompts: "Does your paper rely on new or previously unpublished empirical data from your lab?", "If your paper presents new empirical work, does it include the following statement: “We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study”? It seems to me that both of these apply to the current manuscript (the nove empirical data is the results of the reproducibility assessments).}

We have modified in the resubmission form the answers to these prompts. Therefore, we have also included the “Reporting” subsection in the “Disclosures” section (see p. 7):

>## Reporting
\textcolor{blue}{Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.}

Accordingly, we have included information on how we determine our sample size. We have included the following statements (see p. 8):

### 2023-04-24 submission.Rmd
Revised version

# Method
## Preregistration
The pre-data analysis protocol (https://doi.org/10.17605/OSF.IO/79J2T) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.

@@

## Identification and selection of articles and meta-analyses 
In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search [@lopez-nicolas2021]. Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the random selection process is available at: https://osf.io/cp293/. \textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for `r n_mas_less_10` of the articles included in this report. \textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}

@@

## Retrieval of primary data
In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:

$$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$

with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $(1 - {\alpha/2})\%$ percentile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).

>>>>

# Disclosures
## Preregistration
The pre-data analysis protocol (https://doi.org/10.17605/OSF.IO/79J2T) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.

@@

## Reporting

\textcolor{blue}{Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.}

# Method
## Identification and selection of articles and meta-analyses 
In previous research we identified a pool of 664 meta-analytic reports on clinical psychological interventions published between 2000 and 2020 through a systematic electronic search [@lopez-nicolas2021]. Of this pool, 100 were randomly selected using a random number generator between 1 and the total number of meta-analyses identified. The full search strategies and a summary of the screening process are available at: https://osf.io/z5vrn/, and the workflow of the random selection process is available at: https://osf.io/cp293/. \textcolor{blue}{This sample size was based on our judgement of an acceptable trade-off between informativeness and feasibility.}
From these 100 articles, each independent \textcolor{blue} {pairwise meta-analytic model of aggregate data fitted} on at least 10 primary studies was selected. In case no meta-analysis reported in a paper had at least 10 studies, the meta-analysis with the highest number of primary studies was selected, which was the case for `r n_mas_less_10` of the articles included in this report. \textcolor{blue}{This criterion was established to focus on the main meta-analyses of each paper, based on the assumption that the search strategies would be designed to maximise the number of primary studies included that were related to the main aims of the paper.}

@@

## Retrieval of primary data
In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}^[By primary-level data we mean aggregate data from included primary studies.] effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows: 
$$se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})$$
with $se_i$ being the standard error of the ith effect size, $UB_i$ and $LB_i$ the upper and lower confidence limits of confidence interval for the ith effect size, and $z_{\alpha/2}$ the $(1 - {\alpha/2})\%$ percentile of the standard normal distribution (usually, $z_{\alpha/2} = 1.96$ assuming a two-sided 95% confidence interval).

### 2023-04-24 submission.tex
Revised version

@@

@@

In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}\footnote{By primary-level data we mean aggregate data from included primary studies.} effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:

\[se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})\]

with \(se_i\) being the standard error of the ith effect size, \(UB_i\) and \(LB_i\) the upper and lower confidence limits of confidence interval for the ith effect size, and \(z_{\alpha/2}\) the \((1 - {\alpha/2})\%\) percentile of the standard normal distribution (usually, \(z_{\alpha/2} = 1.96\) assuming a two-sided 95\% confidence interval).

>>>>

\hypertarget{disclosures}{%
\section{Disclosures}\label{disclosures}}

@@

\hypertarget{reporting}{%
\subsection{Reporting}\label{reporting}}

\textcolor{blue}{Below we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.}

@@

In order to be able to reproduce meta-analyses of \textcolor{blue}{aggregate data, primary-level}\footnote{By primary-level data we mean aggregate data from included primary studies.} effects sizes and their associated standard errors are required. These are generally computed from statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the statistics \textcolor{blue}{used to compute primary effect sizes (e.g., means, sd)}; second, we sought for the primary effects sizes \textcolor{blue}{already computed} and their standard errors (or, alternatively, the sampling variances): finally, we sought for the primary effects sizes and their confidence limits, from which the standard errors were approximated as follows:
\[se_i = (\frac{UB_i - LB_i}{2z_{\alpha/2}})\]
with \(se_i\) being the standard error of the ith effect size, \(UB_i\) and \(LB_i\) the upper and lower confidence limits of confidence interval for the ith effect size, and \(z_{\alpha/2}\) the \((1 - {\alpha/2})\%\) percentile of the standard normal distribution (usually, \(z_{\alpha/2} = 1.96\) assuming a two-sided 95\% confidence interval).
